Observation of S-wave scattering of fermions accross a Feshbach resonance

### 2014-12-30 draft1.tex
Experiment section almost done

\subsection{Experimental setup}

@@

\par We then use a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice. Since the initial Fermi gas has a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms are successfully transferred into the 1st excited band of the lattice. We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely. The optimized pulse times are ??FILL IN??
\par We release the atoms from the trap and allow ??FILL IN TIME?? for the two opposite momentum states within the cloud to pass through each other, scattering on the way. For the data taken coming from below the Feshbach resonance, we then simply ramp down the field and image the atoms. For the data taken coming from above the Feshbach resonance, we then ramp the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramp the field back down and image the atoms. We use an imaging pulse of 40$\mu s$.

@@

@@

>>>>

\subsection{Experimental procedure}

@@

\par We then use a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice. Since the initial Fermi gas has a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms are successfully transferred into the 1st excited band of the lattice. We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely. The optimized pulse times are 23$\mu s$ for the first square pulse, 13$\mu s$ off interval, and 12$\mu s$ for the second square pulse. 
\par We release the atoms from the trap and allow 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way. For the data taken coming from below the Feshbach resonance, we then simply ramp down the field and image the atoms. For the data taken coming from above the Feshbach resonance, we then ramp the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramp the field back down and image the atoms. We use an imaging pulse of 40$\mu s$.

@@

We first correct each image for recoil induced detuning using the simulation described above. The simulation gives us a look-up table of observed optical density as a function of atom column density and probe intensity. From our two absorption images we observe the probe intensity and optical density for each pixel. We then use the simulation look-up table in an inverted faction to deduce the column density or, equivalently, the optical depth. An example of the effect of this correction procedure in shown in figure \ref{fig:SampleCorrection}
	\subfigure[]{\includegraphics[scale=0.8]{figure10a}}
	\subfigure[]{\includegraphics[scale=0.8]{figure10b}}
\caption{An example of our absorption image after 6.784ms time of flight. The 1-D lattice is along the horizontal direction at the center of our images. The two large clouds on the left and right are the atoms in the $\pm 2k_r$ momentum orders that passed through each other unscattered. The smaller cloud in the center is the atoms that remained in the lowest band of the lattice after pulsing, and thus obtained no momentum. The thin spread of atoms around these clouds is the atoms that underwent scattering.  a. Raw optical density b. Optical density of the same image after correcting for recoil induced detuning by comparing to simulation}  
\label{fig:SampleCorrection}
\par To improve the signal and compensate for our shot to shot number fluctuations, we take 15 equivalent images for each data point and, after correcting, add them together. We then perform a standard inverse Abel transform to extract the radial atom number dependence from the two dimensional projection we see in our images. The inverse Abel transform assumes a cilyndrical symmetry, which is present in our case, with the axis of symmetry defined by the 1-D lattice. 
\par We then extract the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value. We unscattered number by counting the number of atoms in the two unscattered clouds. We obtain the number of atoms that underwent single scattering by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi radius around the original center of the cloud. This method excludes atoms that underwent multiple scatterings, as those atoms are not bound by momentum concervation to have travelled the same distance from the center as the unscattered clouds in time of flight. The total atom number is the sum of those two.
\par We then use our data to deduce the resonant field value, the width of the resonance, etc. To do this, we must fit our data to a model. From \cite{Chin10}, we have the expression:
a(B)=a_{bg}\left(1-\frac{\Delta}{B-B_0}\right),
where $a$ is the scattering length, $a_{bg}$ is the scattering lenth away from the resonance, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs. Since we are in the low energy regime, the scattering cross-section is given by $\sigma=4\pi a^2$. 
\par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will get scattered when incident on a cloud of atoms with a surface density of $\frac{N}{A}$ is given by $P_{scat}=\sigma \frac{N}{A}$. If this experiment is repeated 1000 times, the number of times the atom will get scattered is expected to be $N_{scat}=1000 \sigma \frac{N}{A}$.  In our case, half the initial cloud, with atoms number $N_{tot}/2$, is incident on the other half of the initial cloud, again with $N_{tot}/2$ atoms. Thus, the number of scattered atoms should be given by $N_{scat}=\frac{N_{tot}}{2} \sigma \frac{N_{tot}}{2}=\sigma \frac{N_{tot}^2}{4A}$, where $A$ is the cross-sectional area of the cloud. Assuming $A$ is constant for all our data, we can absorb the factor of 4A into our definition of $a_{bg}$, along with the $4\pi$, to obtain
\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2.
\par Unfortunately, we cannot fit to this equation directly - camera readout noise is scewed towards the positive, creating an asymetry in detected shot noise for very low and zero atom number pixels. Thus, there is a background number of what looks like scattered atoms in our treatment, giving rise to a background offset $o$ in our data. Thus, the equation we actually fit to is
\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2 + o,
\label{eq13}
where our fit parameters are $\tilde{a}_{bg}$, $\Delta$, $B_0$, and $o$. 

@@

Our final data is presented in figure \ref{fig:fittedFractions}. The red line is a best fit of the model given in eq.\ref{eq13}. The fit parameters we extract are $\tilde{a}_{bg}=1.48e-3$, $\Delta = 8.98$ Gauss, $B_0 = 202.47$ Gauss, and $o=9.00e-5$. The error bars on the fitted data are obtained solely from photon shot noise of both absorption images propagated through our analysis.
The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=202.1\pm0.07$ and $\Delta=7.8\pm0.6$. 
	\includegraphics[scale=0.57]{figure12}
\caption{Scattered fraction over the total atom number as a function of bias field. Green dots represent data taken coming from below the resonance, and blue dots represent the data taken coming from above the resonance. Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit. The four points in the middle were not used in the fit at all, as they are in the regime where the scattering length is large enough for the atoms to behave hydrodynamically and the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.   }  
\label{fig:fittedFractions}
